%iot

En esta sección mostramos una clasificación de los diferentes tipos de IoT existentes. Hemos hecho la clasificación en las diferentes formas posibles de vender un dispositivo IoT, ordenados por el que más aceptación tiene, al que menos. Estos son los diferentes mercados que pueden verse.

Se ha elegido esta forma de clasificar, porque cada dispositivo IoT es diferente y es difícil de predecir su seguridad, de esta forma, se puede observar los diferentes mercados e intentar ajustarse a uno específico.

Esta lista es una de infinitas posibilidades que podrían hacerse.

\begin{itemize}
	\item \textbf{Smart home}: A smart home, or smart house, is a home that incorporates advanced automation systems to provide the inhabitants with sophisticated monitoring and control over the building's functions.\\ The Smart Homes have become a popular search in the internet.\\ More companies are active in this scope than any other application in the IoT field. In the list of recognized gadgets are the names of Nest or AlertMe, as well as a number of multinational corporations such as Philips, Haier, or Belkin. The most common features in a smart home are control lighting, temperature, multi-media, security, window and door operations, as well as many other functions.

	\item \textbf{Wearables}: The wearables are smart electronic devices that can be worn on the body as implant or accessories. These devices show the most significant daily growth, derived from the large number of emerging terminals that are manufactured and marketed daily. Examples such as the smartwatchs of different companies are emerging every day, as well as bands tracking daily activity, etc.

	\item \textbf{Smart city}: A smart city is an urban development vision to integrate information and communication technology to manage a city's assets.\\ For example, manage waste, traffic management, water, urban security and environmental monitoring, making them more efficient and safer, thanks to the Devices and Internet technology of the Things (\ IoT)\\ For these reasons smart cities are searched every day by several users.

	\item \textbf{Smart grid}: A smart grid is an electrical grid which includes a variety of operational and energy measures including smart meters, smart appliances, renewable energy resources, and energy efficient resources.\\
	A future of smart grids is committed to using information on the behavior of electricity suppliers and consumers in an automated way to improve the efficiency, reliability and economy of electricity.

	\item \textbf{Industrial Internet of Things (IIoT)}: The Industrial Internet of Things (IIoT) is the use of Internet Technologies of Things (IoT) in manufacturing.\\ Many market studies such as Gartner or Cisco see in the Internet Industry as the IoT concept with the greatest global potential.

	\item \textbf{Connected car}: A connected car is a car that is equipped with Internet access, and usually also with a wireless local area network. This kind of car provides tools to the driver and to the passangers like gps, movies, temperature control, etc... In some years there will be autonomous car that drive by themselves.

	\item \textbf{Health}: In this field are several devices that has great potencial. These gadgets can help doctors with monitoring pacients and search in the registry to deseases with those syntoms or warn to the near hospital when a monitoring pacient has an attack.

	\item \textbf{Others}: Exists other market for \IoT like agriculture, marketing, advertisment, etc... The differents \IoT widget are useful but less common that above list.
\end{itemize}