\documentclass[a4paper,english,11pt]{article}
% \usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{verbatim}
\usepackage{fancyhdr}
\usepackage{lmodern}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{listing}
\usepackage{adjustbox}
\usepackage{indentfirst}
\usepackage[most]{tcolorbox}
\usepackage{tcolorbox}
\usepackage{lipsum}
%\usepackage{url}
\usepackage[T1]{fontenc}
\usepackage[bookmarks,hyperfootnotes=false,colorlinks=true,urlcolor=black,linkcolor=black,citecolor=black,pagecolor=black,anchorcolor=black,breaklinks=true]{hyperref}% Hiperenlaces

\usepackage{graphicx}
\usepackage{fixme}
\usepackage{lscape}
\usepackage{movie15}
\graphicspath{{images/}}
\DeclareGraphicsExtensions{.png,.pdf,}

% Párrafos
\setlength{\parskip}{8pt}

\begin{document}
	
	\renewcommand*{\thepage}{\roman{page}}
	\newcommand{\IoT}{\textbf{IoT} }
	
	\begin{titlepage}
		\begin{center}
			\vspace*{0,5cm} 
			{\Large \textsc{Universidad Internacional Méndez Pelayo\\}}
			\vspace{3mm}
			{\huge \textbf{Resolución de problemas con metaheurísticos}} \\
			\vspace{1,7cm}
			{\Large \textsc{Testing security Internet of Thing\\}}
			
		\end{center}
		\vspace{12.3cm}
		\begin{table}[!h]
			\Large
			\begin{tabular}{rl}
				\textbf{Author}: & Antonio José Checa Bustos\\
				
			\end{tabular}
		\end{table}
		% \vspace{1,5cm} \\
		% \begin{flushright}
		% {\large \today}
		% \end{flushright}
	\end{titlepage}
	
	
	
	
	\newpage
	\thispagestyle{empty}
	\renewcommand{\contentsname}{Contents}
	\renewcommand{\refname}{References}
	\tableofcontents
	\newpage
	
	\pagestyle{fancy}
	\fancyhead[L]{Testing security IoT}
	% \fancyhead[R]{Antonio José Checa Bustos}
	\fancyfoot[C]{\thepage}
	\renewcommand{\sectionmark}[1]{\markboth{\textbf{\thesection. #1}}{}}
	\renewcommand*{\thepage}{\arabic{page}}
	\setcounter{page}{1}
	
	\section{Introduction}
	\label{sec:intro}
	\input{intro.tex}	
	
	\newpage
	
	\section{Articles}
	\label{sec:articulos}
	\input{articulos.tex}	
	
	\newpage
	
	\section{Companies}
	\label{sec:empresas}
	\input{empresas.tex}
	
	\newpage
	
	\section{PenTesting}
	\label{sec:pentesting}
	\input{pentesting.tex}
	
	\newpage
	
	\section{IoT classification}
	\label{sec:iot}
	\input{iot.tex}
	
	\newpage
	
	\section{Conclusion}
	\label{sec:artcomp}
	\input{artcom.tex}
	
	\newpage
	
	\bibliographystyle{ieeetr}	
	\begin{thebibliography}{9}	
		
		\bibitem{Paper0}
		Craigen, D., Diakun-Thibault, N., \& Purse, R. (2014). Defining cybersecurity. Technology Innovation Management Review, 4(10).
		
		\bibitem{Paper}
		Amoroso, E. 2006. Cyber Security. New Jersey: Silicon Press.
		
		\bibitem{IoT1}
		S. Haller S. Karnouskos and C. Schroth "The Internet of Things in an Enterprise Context " in Future Internet-FIS 2008 Lecture Notes in Computer Science Vol. 5468 2009 pp 14-28.
		
		\bibitem{IoT2}
		A. C. Sarma and J. Girão "Identities in the Future Internet of Things " in Wireless Personal Communications 49.3 2009 pp. 353-363.
		
		\bibitem{IoT3}
		Roberto Minerva Abiy Biru "Towards a Definition of the Internet of Things " IEEE IoT Initiative white paper.
		
		\bibitem{Paper1} 		
		Jonathan Charity Talwana, Huang Jian Hua, \href{http://ieeexplore.ieee.org/document/7917092/}{Smart World of Internet of Things (IoT) and Its Security Concerns} (15-18 Dec. 2016) 4 May 2017
		
		\bibitem{Data1}
		Gubbi, J., Buyya, R., Marusic, S., \& Palaniswami, M. (2013). Internet of Things (IoT): A vision, architectural elements, and future directions. Future generation computer systems, 29(7), 1645-1660.
		
		\bibitem{Paper2} 
		Eike Steffen Reetz, Daniel Kuemper, Klaus Moessner, \href{http://ieeexplore.ieee.org/document/6582811/}{How to Test IoT-based Services before Deploying them into Real World} (16-18 April 2013) Online - 20 August 2013
		
		\bibitem{Paper3}
		Giménez, P., Molina, B., Palau, C. E., \& Esteve, M. (2013, October). \href{http://ieeexplore.ieee.org/document/6721820/}{SWE simulation and testing for the IoT.} In Systems, Man, and Cybernetics (SMC), 2013 IEEE International Conference on (pp. 356-361). IEEE.
		
		\bibitem{Paper9}
		Gubbi, J., Buyya, R., Marusic, S., \& Palaniswami, M. (2013). Internet of Things (IoT): A vision, architectural elements, and future directions. Future generation computer systems, 29(7), 1645-1660.
				
		\bibitem{Paper8}
		Lake, D., Milito, R., Morrow, M., \& Vargheese, R. (2014). Internet of things: Architectural framework for ehealth security. Journal of ICT Standardization, River Publishing, 1.
		
		\bibitem{Paper11}
		Che, X., \& Maag, S. (2014). Testing protocols in Internet of Things by a formal passive technique. Science China Information Sciences, 57(3), 1-13.
		
		\bibitem{Presentation1}
		Miessler, D. (2015). IoT Attack Surface Mapping.
		
		\bibitem{Paper12}
		Kirichek, R., \& Koucheryavy, A. (2016). Internet of things laboratory test bed. In Wireless Communications, Networking and Applications (pp. 485-494). Springer India.
		
		\bibitem{Paper4} 
		Erik Jan Marinissen, Yervant Zorian, Mario Konijnenburg, \href{http://ieeexplore.ieee.org/document/7519331/}{IoT: Source of test challenges} (23-27 Mayo 2016) 25 Julio 2016
		
		\bibitem{Paper10}
		Kolias, C., Stavrou, A., Voas, J., Bojanova, I., \& Kuhn, R. (2016). Learning Internet-of-Things Security" Hands-On". IEEE Security \& Privacy, 14(1), 37-46.
		
		\bibitem{Paper5} 
		Umar Ahsan, Abdul Bais, \href{http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=7815042&tag=1}{A Review on Big Data Analysis and Internet of Things} (10-13 Octubre 2016) Publicado el 16 de Enero 2017
		
		\bibitem{Paper6} 
		Salvador Pérez, Juan A. Martínez, Antonio F. Skarmeta, Márcio Mateus, Bruno Almeida, Pedro Maló, \href{http://ieeexplore.ieee.org/document/7845504/}{ARMOUR: Large-scale experiments for IoT security \& trust}
		(12-14 Dec. 2016) publicado el 9 de febrero 2017
		
		\bibitem{Paper7} 
		Ruth M. Ogunnaike; Brent Lagesse, \href{http://ieeexplore.ieee.org/document/7917633/}{Toward consumer-friendly security in smart environments}, (13-17 March 2017), 4 May 2017
		
		\bibitem{ethicalHacking}
		Saleem, S. A. (2006, September). Ethical hacking as a risk management technique. In Proceedings of the 3rd annual conference on Information security curriculum development (pp. 201-203). ACM.
		
		\bibitem{Hacking1}
	    Julia Allen, Alan Christie, William Fithen, John ?McHugh, Jed Pickel, Ed Stoner. (2000). "State of the Practice of Intrusion Detection Technologies". http://www.sei.cmu.edu/publications/documents/99.reports/99tr028/99tr028title.html.
	    
	    \bibitem{Hacking2}
        "NSA Glossary of Terms Used in Security and Intrusion Detection". http://www.sans.org/newlook/resources/glossary.htm.
        
        \bibitem{Hacking3}
         Michael Gregg, Certified Ethical Hacker
	\end{thebibliography}
	
\end{document}